### 2023-12-27 sections/5-discussion.tex
minor updates to discussion

\section{Discussion and Future Work}
\label{sec:discussion}

@@

As seen in Figures~\ref{fig:results:random-lfd}~and~\ref{fig:results:sift-lfd}, the LFD of the Random dataset is much higher than that of Sift.
This is unsurprising, given that the Random dataset is, by definition, uniformly distributed, while Sift is not.
On the Random dataset, CAKES's algorithms' throughputs decrease linearly as the multiplier increases, while with Sift, GreedySieve and Sieve both exhibit nearly constant throughput.
While Repeated $\rho$-NN does not exhibit near-constant throughput with Sift, the throughput decreases much more slowly than it does with the Random dataset.
Since these two datasets have the same cardinality and embedding dimension, the aforementioned discrepancies show the effect of a manifold structure on algorithm performance.
We emphasize that even though CAKES's algorithms are slower on the Random dataset, their recalls remain perfect at all multipliers.

@@

We also note that the CAKES algorithm with the best throughput varies by dataset.
For example, on Glove-25, Repeated $\rho$-NN exhibits the highest throughput of any CAKES algorithm, despite having the lowest throughput of the three on Sift and Fashion-Mnist. 
On Silva, Repeated $\rho$-NN is comparable to the other CAKES algorithms at low multipliers, but becomes the fastest at the higher multipliers. 
When we view these results in light of the LFD plots in Section~\ref{subsec:lfd-results}, we realize that Repeated $\rho$-NN appears to be the fastest CAKES algorithm on datasets where a large proportion of the dataset has a very low LFD (i.e., near $2$), such as Glove-25 and Silva. 
This trend is unsurprising, given that Repeated $\rho$-NN relies on a low LFD around the query in order to quickly estimate the correct radius for $k$ hits. 
These findings suggest that Repeated $\rho$-NN is the most ``sensitive'' to the manifold structure of the dataset.
Exploring this sensitivity is a potential avenue for future investigation, as it remains to be determined at what LFD Repeated $\rho$-NN transitions away from being the fastest CAKES algorithm, and whether this transition is sharp.

While the fastest CAKES algorithm varies by dataset, we observe that on all three ANN-benchmark datasets (Fashion-mnist, Glove-25, and Sift), GreedySieve and Sieve show nearly constant throughput as the cardinality increases.
This observation warrants further investigation, but it is especially promising given that GreedySieve and Sieve consistently outperform linear search for high cardinalities.
Finally, we emphasize that the variation in performance of our algorithms across different datasets and cardinalities supports our use of an auto-tuning function (as discussed in Section~\ref{subsec:methods:auto-tuning}) to select the best algorithm for a given dataset.
Given trends such as the performance of Repeated $\rho$-NN with low LFD, we suspect that a more sophisticated auto-tuning function could be developed to select the fastest algorithm based on the properties of the dataset.

We also stress that CAKES's algorithms are designed to work well for \emph{big} data, and our results support this claim;
we observe that while linear search can outperform CAKES on datasets with small cardinality, CAKES always overtakes linear search at a large enough cardinality for each of the ANN-benchmarks' datasets we tested.
Moreover, we observe that CAKES's algorithms outperform linear search at a lower cardinality when the dataset has a lower LFD.
For example, Sift has much higher LFD than Fashion-mnist and Glove-25, and we observe that CAKES overtakes linear search at a cardinality of $10^7$ for Sift, as opposed to about $10^5$ and $10^6$ for Fashion-mnist and Glove-25, respectively.
For the Random dataset, which has the highest LFD, CAKES's algorithms \emph{never} outperform linear search.
These observations support our claim that CAKES performs well on datasets that arise from constrained generating phenomena, even as the cardinalities of these datasets grow exponentially.

>>>>

\section{Discussion and Future Work}
\label{sec:discussion-and-future-work}

@@

As seen in Figures~\ref{fig:results:random-lfd}~and~\ref{fig:results:sift-lfd}, the LFD of the Random dataset is much higher than that of Sift.
This is unsurprising, given that the Random dataset is, by definition, uniformly distributed, while Sift is not.
On the Random dataset, CAKES's algorithms' throughputs decrease linearly as the multiplier increases, while with Sift, Depth-First Sieve and Breadth-First Sieve both exhibit nearly constant throughput.
While Repeated $\rho$-NN does not exhibit near-constant throughput with Sift, the throughput decreases much more slowly than it does with the Random dataset.
Since these two datasets have the same cardinality and embedding dimension, the aforementioned discrepancies show the effect of a manifold structure on algorithm performance.
We emphasize that even though CAKES's algorithms are slower on the Random dataset, their recalls remain perfect at all multipliers.

@@

We also note that the CAKES algorithm with the best throughput varies by dataset.
For example, on Glove-25, Repeated $\rho$-NN exhibits the highest throughput of any CAKES algorithm, despite having the lowest throughput of the three on Sift and Fashion-Mnist. 
On Silva, Repeated $\rho$-NN is comparable to the other CAKES algorithms at low multipliers, but becomes the fastest at the higher multipliers. 
When we view these results in light of the LFD plots in Section~\ref{sec:results:lfd-of-datasets}, we realize that Repeated $\rho$-NN appears to be the fastest CAKES algorithm on datasets where a large proportion of the dataset has a very low LFD (i.e., near $2$), such as Glove-25 and Silva. 
This trend is unsurprising, given that Repeated $\rho$-NN relies on a low LFD around the query in order to quickly estimate the correct radius for $k$ hits. 
These findings suggest that Repeated $\rho$-NN is the most ``sensitive'' to the manifold structure of the dataset.
Exploring this sensitivity is a potential avenue for future investigation, as it remains to be determined at what LFD Repeated $\rho$-NN transitions away from being the fastest CAKES algorithm, and whether this transition is sharp.

While the fastest CAKES algorithm varies by dataset, we observe that on all three ANN-benchmark datasets (Fashion-Mnist, Glove-25, and Sift), Depth-First Sieve and Breadth-First Sieve show nearly constant throughput as the cardinality increases.
This observation warrants further investigation, but it is especially promising given that Depth-First Sieve and Breadth-First Sieve consistently outperform linear search for high cardinalities.
Finally, we emphasize that the variation in performance of our algorithms across different datasets and cardinalities supports our use of an auto-tuning function (as discussed in Section~\ref{sec:methods:auto-tuning}) to select the best algorithm for a given dataset.
Given trends such as the performance of Repeated $\rho$-NN with low LFD, we suspect that a more sophisticated auto-tuning function could be developed to select the fastest algorithm based on the properties of the dataset.

We also stress that CAKES's algorithms are designed to work well for \emph{big} data, and our results support this claim;
we observe that while linear search can outperform CAKES on datasets with small cardinality, CAKES always overtakes linear search at a large enough cardinality for each of the ANN-benchmarks' datasets we tested.
Moreover, we observe that CAKES's algorithms outperform linear search at a lower cardinality when the dataset has a lower LFD.
For example, Sift has much higher LFD than Fashion-Mnist and Glove-25, and we observe that CAKES overtakes linear search at a cardinality of $10^7$ for Sift, as opposed to about $10^5$ and $10^6$ for Fashion-Mnist and Glove-25, respectively.
For the Random dataset, which has the highest LFD, CAKES's algorithms \emph{never} outperform linear search.
These observations support our claim that CAKES performs well on datasets that arise from constrained generating phenomena, even as the cardinalities of these datasets grow exponentially.
